Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Latest
Latest version

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/hw.cxl}
\end{code}
\caption{[hw.cxl] Non-blocking queue.}
\label{fig:hw}
\end{figure}

So far we have concentrated on critical sections to synchronize multiple
processes.  Certainly, preventing multiple processes from accessing
certain code at the same time simplifies how to think about synchronization.
However, it can lead to starvation.  Even in the absence of starvation,
if some process is slow for some reason while being in the critical section,
the other processes have to wait for it to finish the critical section.
In this chapter, we will have a brief look at how one can develop concurrent
code in which processes never have to wait for other processes.
For this, we will revisit the producer/consumer problem, in which a
set of processes are producing items and a set of processes are
consuming items.

The code in Figure~\ref{fig:hw} is based on code developed by Herlihy and
Wing~\cite{HW}.  It uses two interlock instructions:
\begin{itemize}
\item \texttt{inc(p)}: atomically increments \texttt{\^{}p} and returns
the old value;
\item \texttt{swap(p)}: sets \texttt{\^{}p} to \texttt{()} and returns
the old value.
\end{itemize}
